\documentclass{article}
\usepackage{amsmath,amssymb,amsfonts,amsthm}

\begin{document}

\providecommand{\pr}[1]{\ensuremath{\Pr\left(#1\right)}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\newcommand{\solution}{\noindent \textbf{solution: }}

\textbf{Question 11.16.4.9}\\
If 4-digit numbers greater than 5,000 are randomly formed from the digits 0, 1, 3, 5, and 7, what is the probability of forming a number divisible by 5 when:
\begin{enumerate}
    \item The digits are repeated?
    \item The repetition of digits is not allowed?
\end{enumerate}

\solution
Let $X$ be a random variable such that:
\begin{align}
	X = \begin{cases}
		0 & n \not\equiv 0 \pmod{5}\\
		1 & n \equiv 0 \pmod{5}\end{cases}
\end{align}

Let $X_{1},X_{2},X_{3},X_{4}$ be the first,second,third and fourth digits of X respectively.

Let's solve each part separately. \\

\textbf{(i) Repetition of digits}\\
Let number of favourable outcomes be N(A) and total outcomes be N(T).

For X $>$ 5000,
\begin{enumerate}
	\item $X_{1}$ must be 5 or 7.
	\item $X_{2},X_{3},X_{4}$ can be 0,1,3,5,7.
\end{enumerate}
We must also exclude the case of 5000.
Hence,
\begin{align}
	N(T)=(2*5*5*5)-1 \\
	\implies N(T)=249
\end{align}

For n to be greater than 5000 and also divisble by 5:
\begin{enumerate}
	\item $X_{1}$ must be 5 or 7.
	\item $X_{2},X_{3}$ can be 0,1,3,5,7.
	\item $X_{4}$ must be 0 or 5.
\end{enumerate}
Here also we must exclude the case of 5000.
\begin{align}
	N(A)=(2*5*5*2)-1 \\
	\implies N(A)=99
\end{align}

With this information we can find the required answer,
\begin{align}
	\pr{X=1}=\frac{N(A)}{N(T)}\\
	\implies \pr{X=1}=\frac{33}{83}
\end{align}



\textbf{(ii) No Repetition of Digits}\\
Let number of favourable outcomes be N(B) and total outcomes be N(T).

For X $>$ 5000,

\begin{enumerate}
	\item $X_{1}$ must be 5 or 7.\\
	\item $X_{2},X_{3},X_{4}$ have no constraints.
\end{enumerate}

Hence,
\begin{align}
	N(T)=(2*4*3*2) \\
	\implies N(T)=48
\end{align}

For n $>$ 5000 and also divisble by 5:

\begin{align}
	X_{4} = \begin{cases}
		0 & X_{1}=5 \\
		5,0 & X_{1}=7
	\end{cases}
\end{align}

Hence,
\begin{align}
	N(B)=(1*3*2*1)+(1*3*2*2) \\
	\implies N(B)=18
\end{align}

With this information we can find the required answer,
\begin{align}
	\pr{X=1}=\frac{N(B)}{N(T)}\\
	\implies \pr{X=1}=\frac{3}{8}
\end{align}

\end{document}
